SIR-RL: Reinforcement Learning for Optimized Policy Control during Epidemiological Outbreaks in Emerging Market and Developing Economies

### 2024-03-24 paper_draft/main.tex
fixes in 2.6

\subsection{Modelling Normalized GDP with Stringency}
Now, that a relation between $\beta$ and $s(t)$ is set up, it must be investigated how stringency index affects the normalized gross domestic product (GDP)~\cite{OECDNormalizedGDP,OECDNormalizedGDP2}. To do this a polynomial equation of the third degree is fitted to the data points $f(x) = a x^3 + b x^2 + c x + d = y$, here, $x$ is the $s(t)$ stringency at time $t$, and $y$ the normalized GDP, and we minimize the squared error to find the values of coefficients $a, b, c, d$. For India after fitting a 3 degree polynomial, the following equation is obtained:
\begin{equation}
    \begin{split}
      \textrm{normalized\_GDP} = -5.96640236 \times 10^{-5} s^{3} + 6.65064332 \times 10^{-3} s^{2} - 2.23109924 \times 10^{-1} s^{1} \\
    + 1.01357226 \times 10^{2}
    \end{split}
    \label{eq:gdp_modelled_with_stringency_IND}
\end{equation}

>>>>

\subsection{Modelling Normalized GDP with Stringency}
Now, that a relation between $\beta$ and $s(t)$ is set up, it must be investigated how stringency index affects the normalized gross domestic product (GDP)~\cite{OECDNormalizedGDP,OECDNormalizedGDP2}. To do this a polynomial equation of the third degree is fitted to the data points $f(x) = a x^3 + b x^2 + c x + d = y$, here, $x$ is the stringency ($s$), and $y$ the normalized GDP, and we minimize the squared error to find the values of coefficients $a, b, c, d$. For India after fitting a 3 degree polynomial, the following equation is obtained:
\begin{equation}
    \begin{split}
      \textrm{normalized\_GDP} = -5.96640236 \times 10^{-5} s^{3} + 6.65064332 \times 10^{-3} s^{2} - 2.23109924 \times 10^{-1} s^{1} \\
    + 1.01357226 \times 10^{2}
    \end{split}
    \label{eq:gdp_modelled_with_stringency_IND}
\end{equation}
